Intrusion Detection with \\ Genetic Algorithms and Fuzzy Logic

### 2013-11-17 Talk/Presentation.tex
Added a better trapezoid figure that has an example, added results for the genetic algorithm, worked on References slide.

% The text in square brackets is the short version of the date if you need that.
\date[December '13] % (optional)
{December 2013 \\ UMM CSci Senior Seminar Conference}

@@

\begin{frame}
  \frametitle{Measuring the Probability of a Record Being an Attack}

  \begin{columns}
  \begin{column}{0.6\textwidth}
  \includegraphics[width=0.95\textwidth]{../TrapezoidFigure.pdf}
  \end{column}

  \begin{column}{0.4\textwidth}
  Example:
  \begin{itemize}
  	\item Feature: duration (length of the activity in seconds).
  	\item a=1, b=3, c=5, d=7
  	\item The length of the activity is 6 seconds (between c and d).
  	\linespace
  	\item prob = $\frac{d-\textrm{data}}{d-c}$ = $\frac{7-6}{7-5}$ = 0.5
  \end{itemize}

@@

\begin{figure}
\begin{small}

\begin{tabular}{|cccc|c|cccc|c|} \hline
010 & 011 & 100 & 101   & ...... & 010 & 011 & 101 & 111   & DoS\\
a=2 & b=3 & c=4 & d=5   & ...... & a=2 & b=3 & c=5 & d=7   &\\ 
    &     & Block 1&    &        &     & Block 12& &       & Type\\
\hline\end{tabular}
\end{small}
\end{figure}

@@

\begin{frame}
  \frametitle{Results}
\begin{table}
\begin{small}
\begin{tabular}{cccccccc}
& & \multicolumn{5}{ c }{Predicted} \\
& & Normal & Probe & DoS & U2R & R2L & \% Correct \\ \cline{3-8}
\multicolumn{1}{ c }{\multirow{2}{*}{Actual} } &
\multicolumn{1}{ c| }{Normal} & 42138 & 1421 & 15835 & 486 & 713 & 69.5\\
\multicolumn{1}{ c }{} &
\multicolumn{1}{ c| }{Probe} & 398 & 2963 & 654 & 2 & 149 & 71.1 \\
\multicolumn{1}{ c }{\multirow{2}{*}{} } &
\multicolumn{1}{ c| }{Dos} & 921 & 432 & 228489 & 1 & 10 & 99.4\\
\multicolumn{1}{ c }{} &
\multicolumn{1}{ c| }{U2R} & 146 & 21 & 8 & 43 & 10 & 18.9\\
\multicolumn{1}{ c }{} &
\multicolumn{1}{ c| }{R2L} & 11191 & 578 & 3398 & 141 & 881 & 5.4\\

\multicolumn{1}{ c }{} &
\multicolumn{1}{ c| }{} & & & & & & \\

\multicolumn{1}{ c }{\% Correct} &
\multicolumn{1}{ c| }{} & 76.9 & 54.7 & 92.0 & 6.4 & 50.0 \\
\end{tabular}
\end{small}
\end{table}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Conclusions]{Conclusions}

@@

\begin{itemize}
  \item The use of genetic algorithms and fuzzy logic in intrusion detection are effective ways of detecting attacks.
  \item The fuzzy genetic algorithm had a higher detection rate than a decision tree algorithm in most cases.
  \item Fuzzy genetic algorithms are good at detecting unknown attacks.
\end{itemize}

@@

@@

>>>>

% The text in square brackets is the short version of the date if you need that.
\date[December 2013] % (optional)
{December 2013 \\ UMM CSci Senior Seminar Conference}

@@

\begin{frame}
  \frametitle{Measuring the Probability of a Record Being an Attack}
	\begin{itemize}	
	\item Feature: duration, 6 seconds.
	\end{itemize}
%  \begin{columns}
%  \begin{column}{0.6\textwidth}
  \includegraphics[width=0.95\textwidth]{../trapFigExample.pdf}
%  \end{column}

%  \begin{column}{0.4\textwidth}
%  Example:
%  \begin{itemize}
%  	\item Feature: duration (length of the activity in seconds).
%  	\item a=1, b=3, c=5, d=7
%  	\item The length of the activity is 6 seconds (between c and d).
%  	\linespace
%  	\item prob = $\frac{d-\textrm{data}}{d-c}$ = $\frac{7-6}{7-5}$ = 0.5
%  \end{itemize}

%  \end{column}
%  \end{columns}
\end{frame}

@@

\begin{figure}
\begin{small}
\begin{tabular}{|cccc|c|cccc|c|} \hline
010 & 011 & 100 & 101   & ...... & 010 & 011 & 101 & 111   & DoS\\
a=2 & b=3 & c=4 & d=5   & ...... & a=2 & b=3 & c=5 & d=7   &\\ 
    &     & Block 1&    &        &     & Block 12& &       & Type\\
\hline\end{tabular}
\caption{Based on [Jongsuebsuk-Wattanapongsakorn-Charnsripinyo, 2013]}
\end{small}
\end{figure}

@@

\begin{frame}
  \frametitle{Results}
%\begin{table}
%\begin{small}
%\begin{tabular}{cccccccc}
%& & \multicolumn{5}{ c }{Predicted} \\
%& & Normal & Probe & DoS & U2R & R2L & \% Correct \\ \cline{3-8}
%\multicolumn{1}{ c }{\multirow{2}{*}{Actual} } &
%\multicolumn{1}{ c| }{Normal} & 42138 & 1421 & 15835 & 486 & 713 & 69.5\\
%\multicolumn{1}{ c }{} &
%\multicolumn{1}{ c| }{Probe} & 398 & 2963 & 654 & 2 & 149 & 71.1 \\
%\multicolumn{1}{ c }{\multirow{2}{*}{} } &
%\multicolumn{1}{ c| }{Dos} & 921 & 432 & 228489 & 1 & 10 & 99.4\\
%\multicolumn{1}{ c }{} &
%\multicolumn{1}{ c| }{U2R} & 146 & 21 & 8 & 43 & 10 & 18.9\\
%\multicolumn{1}{ c }{} &
%\multicolumn{1}{ c| }{R2L} & 11191 & 578 & 3398 & 141 & 881 & 5.4\\

%\multicolumn{1}{ c }{} &
%\multicolumn{1}{ c| }{} & & & & & & \\

%\multicolumn{1}{ c }{\% Correct} &
%\multicolumn{1}{ c| }{} & 76.9 & 54.7 & 92.0 & 6.4 & 50.0 \\
%\end{tabular}
%\end{small}
%\end{table}
	\begin{figure}
  \includegraphics[width=0.95\textwidth]{../resultsForGA.JPG}
  \caption{From [Hoque-Mukit-Bikas, 2012]}
  	\end{figure}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Conclusions]{Conclusions}

@@

\begin{itemize}
  \item The use of genetic algorithms and fuzzy logic in intrusion detection are effective ways of detecting attacks.
  \item The genetic algorithm had a high detection rate for denial of service attacks.
  \item The fuzzy genetic algorithm had a higher detection rate than a decision tree algorithm in most cases.
  \item Fuzzy genetic algorithms are good at detecting unknown attacks.
\end{itemize}

@@

	\begin{small}
	\bibitem{6496342}
Jongsuebsuk, P. and Wattanapongsakorn, N. and Charnsripinyo, C.
\newblock Network intrusion detection with Fuzzy Genetic Algorithm for unknown attacks.
\newblock In \emph{2013 International Conference on Information Networking (ICOIN)}, pages 1-5, 2013.

	\bibitem{6559603}
Jongsuebsuk, P. and Wattanapongsakorn, N. and Charnsripinyo, C.
\newblock Real-time intrusion detection with fuzzy genetic algorithm.
\newblock In \emph{2013 10th International Conference on Electrical Engineering/Electronics, Computer, Telecommunications and Information Technology (ECTI-CON)}, pages 1-6, 2013.

	\bibitem{DBLP:journals/corr/abs-1204-1336}
Mohammad Sazzadul Hoque, Md. Abdul Mukit, Md. Abu Naser Bikas.
\newblock An Implementation of Intrusion Detection System Using Genetic Algorithm.
\newblock \emph{CoRR}, abs/1204.1336, 2012.
	\end{small}

@@

  	\linespace

  	\begin{center}
  	\begin{small}
  	See my Senior Seminar paper for additional references.
  	\end{small}
  	\end{center}
